Weather Data Integration and Assimilation System\\

### 2020-02-10 results/sec_3-observations.tex
Change table font size
Reduce table font size all
change to footnotesize table font size
Change Full Test

%Following \ref{subse:obs_test_plan_all_60min}, \ref{subse:obs_test_plan_all_30min}, \ref{subse:obs_test_plan_all_15min} and \ref{subse:obs_test_plan_all_auto_15min} sections
\db{Sections \ref{subse:obs_test_plan_all_60min} to \ref{subse:obs_test_plan_all_auto_15min} discuss} the observations collected with performing the Full test plan (also known as All test plan) over 60 minutes (24 data points), 30 minutes (48 data points) and 15 minutes (96 data points) by variate the request size. Then another performance test with enabling Auto Scaling as explained in \ref{subse:test_plan_metrics} for high resource utilized microservice.

\subsection{Full Test with hourly data (24 Request Size)}
\label{subse:obs_test_plan_all_60min}

\dbc{"Full Test"is a not a good term}

@@

\dbc{Fonts for tables should be 10pt.}

\begin{table}[]
\begin{tabulary}{\linewidth}{|L|C|C|C|C|C|C|C|C|}
\hline
Label & \# Samples & Avg & Min & Max & 90\% Line & Std. Dev. & Error \% & RPS \\ \hline
Insert Timeseries & 71826 & 28 & 13 & 2773 & 31 & 58.74 & 0.00\% & 40.5 \\ \hline
Retrieve Timeseries & 71796 & 8 & 7 & 242 & 10 & 4.18 & 0.00\% & 40.7 \\ \hline
Insert Grid & 7982 & 23 & 21 & 126 & 26 & 4.23 & 0.06\% & 4.5 \\ \hline
Retrieve Grid & 7979 & 68 & 59 & 238 & 75 & 10.11 & 0.00\% & 4.5 \\ \hline
Query: Location & 71804 & 3 & 2 & 109 & 3 & 1.52 & 0.00\% & 40.5 \\ \hline
\textbf{TOTAL} & 311182 & 127 & 0 & 2773 & 503 & 207.80 & 0.00\% & 175.4 \\ \hline
\end{tabulary}
\caption{Throughput and Latency of All test cases with 60min data}
\label{tab:obs_all_60_min_summary}
\end{table}
Insert Timeseries performed over Scalar and Vector data types with each request send with 24 data points. On average it takes 28ms to insert data into the \acrshort{wdias}, and up to 90\% percentile inserted data within 31ms. Noticeably it has 0\% of errors which means that all the request are completed successfully. On average, \acrshort{wdias} handled 40.5 \acrshort{rps} with the given workload. The performance of the Retrieve of Scalar and Vector Timeseries are similar to insert timeseries due to it depends on it.
On the other hand, Insert Grid Timeseries data perform with 23ms with almost all the request perform within same amount of time, hence the standard deviation is smaller. Retrieve Grid Timeseries data perform the same but with bit higher value of latency of 68ms. Both of insert and retrieve grid timeseries data have 4.5 \acrshort{rps} since it only get 10\% of the number of request per given time via the test plan as explain in the data ration in \ref{se:test_plan}.

@@

\subsection{Full Test with 30min data (48 Request Size)}
\label{subse:obs_test_plan_all_30min}
This section \ref{subse:obs_test_plan_all_30min} discussed about the All test plan performance with 30 minutes data which means 48 data points per each request in Scalar and Vector timeseries, and 48 ASCII Grid files per each insert request. It performed round up to 311k of sample requests which is almost similar to \ref{subse:obs_test_plan_all_60min} processed samples.
\begin{table}[]
\begin{tabulary}{\linewidth}{|L|C|C|C|C|C|C|C|C|}
\hline
Label & \# Samples & Average & Min & Max & 90\% Line & Std. Dev. & Error \% & RPS \\ \hline
Insert Timeseries & 71759 & 29 & 14 & 1699 & 32 & 50.97 & 0.00\% & 40.5 \\ \hline
Retrieve Timeseries & 71730 & 9 & 7 & 1033 & 10 & 6.04 & 0.00\% & 40.6 \\ \hline
Insert Grid & 7972 & 44 & 40 & 162 & 49 & 8.17 & 0.08\% & 4.5 \\ \hline
Retrieve Grid & 7971 & 81 & 67 & 284 & 93 & 15.15 & 0.00\% & 4.5 \\ \hline
Query: Location & 71734 & 3 & 2 & 110 & 3 & 1.90 & 0.00\% & 40.5 \\ \hline
TOTAL & 310878 & 129 & 0 & 1699 & 503 & 207.10 & 0.00\% & 175.3 \\ \hline
\end{tabulary}
\caption{Throughput and Latency of All test cases with 30min data}
\label{tab:obs_all_30_min_summary}
\end{table}
\ref{tab:obs_all_30_min_summary} shows the response latency summary details and \acrshort{rps} as explained in \ref{subse:obs_test_plan_all_60min}. And the results are almost similar to the observations in \ref{tab:obs_all_60_min_summary}. This implies that, even the request size is increased, the \acrshort{wdias} can perform better same as the with smaller size of data.

@@

\subsection{Full Test with 15min data (96 Request Size)}
\label{subse:obs_test_plan_all_15min}
This section \ref{subse:obs_test_plan_all_15min} discussed about the All test plan performance with 15 minutes data which means 96 data points per each request in Scalar and Vector timeseries, and 96 ASCII Grid files per each insert Grid timeseries request. These requests are four times larger than the \ref{subse:obs_test_plan_all_60min} request size. It performed approximately 311k of sample requests which is almost similar to \ref{subse:obs_test_plan_all_30min} processed samples.
\begin{table}[]
\begin{tabulary}{\linewidth}{|L|C|C|C|C|C|C|C|C|}
\hline
Label & \# Samples & Average & Min & Max & 90\% Line & Std. Dev. & Error \% & RPS \\ \hline
Insert Timeseries & 71775 & 30 & 12 & 1719 & 41 & 51.71 & 0.00\% & 40.5 \\ \hline
Retrieve Timeseries & 71736 & 23 & 8 & 1623 & 32 & 50.18 & 0.00\% & 40.6 \\ \hline
Insert Grid & 7975 & 91 & 77 & 279 & 112 & 19.58 & 1.42\% & 4.5 \\ \hline
Retrieve Grid & 7972 & 118 & 80 & 876 & 165 & 56.15 & 0.00\% & 4.5 \\ \hline
Query: Location & 71749 & 3 & 2 & 130 & 4 & 2.32 & 0.00\% & 40.5 \\ \hline
\textbf{TOTAL} & 310934 & 134 & 0 & 1719 & 503 & 206.40 & 0.04\% & 175.4 \\ \hline
\end{tabulary}
\caption{Throughput and Latency of All test cases with 15min data}
\label{tab:obs_all_15_min_summary}
\end{table}
\ref{tab:obs_all_15_min_summary} shows the response latency summary details and \acrshort{rps} as same as explained in \ref{subse:obs_test_plan_all_30min}. And the latency observations are increased by some amount when compared to the observations in \ref{tab:obs_all_30_min_summary}. Noticeably retrieving latency of all type of data types increased by considerable amount. Same following the trend, standard deviation of retrieve timeseries data increased my considerable amount for all the types. We can assume that more writing to the databases affected on reads as well. Event the request data size increased by 4x time, the \acrshort{wdias} were able to handle them without any significant performance issues. And the system able to provide the same throughput as \ref{tab:obs_all_30_min_summary}.

@@

\subsection{Full Load test with \acrfull{k8s} auto pod scaling}
\label{subse:obs_test_plan_all_auto_15min}
This section \ref{subse:obs_test_plan_all_auto_15min} discussed about the All test plan performance with 15 minutes data which means 96 data points per each request in Scalar and Vector timeseries, and 96 ASCII Grid files per each insert Grid timeseries request. These requests are four times larger than the \ref{subse:obs_test_plan_all_60min} request size. It performed approximately 311k of sample requests which is almost similar to \ref{subse:obs_test_plan_all_15min} processed samples.
Other than that, this test plan runs with enabling \acrshort{k8s} Auto Scaling for the high resource utilized microservice as explained in the \ref{subse:test_plan_metrics}. With the test load used for the performance test, import-ascii-grid-upload microservice is using lots of CPU, and adapter-grid microservice is using lots of Memory. During this test plan, \acrshort{wdias} start with the auto scaling enabled for import-ascii-grid-upload microservice. Since adapter-grid is a consistence service for storing netCDF files, it is not possible to auto scale, since \acrshort{eks} does not support multiple read write support volumes \cite{LinuxFoundationPersistentKubernetes}.

\begin{table}[]
\begin{tabulary}{\linewidth}{|L|C|C|C|C|C|C|C|C|}
\hline
Label & Samples & Avg & Min & Max & 90\% Line & Std. Dev. & Error \% & RPS \\ \hline
Insert Timeseries & 71727 & 34 & 13 & 1777 & 27 & 118.78 & 0.00\% & 40.5 \\ \hline
Retrieve Timeseries & 71693 & 7 & 5 & 1608 & 9 & 18.72 & 0.00\% & 40.5 \\ \hline
Insert Grid & 7968 & 87 & 77 & 233 & 98 & 14.07 & 0.18\% & 4.5 \\ \hline
Retrieve Grid & 7965 & 89 & 63 & 1694 & 110 & 37.79 & 0.00\% & 4.5 \\ \hline
Query: Location & 71704 & 1 & 0 & 203 & 2 & 2.05 & 0.00\% & 40.5 \\ \hline
\textbf{TOTAL} & 310734 & 130 & 0 & 1777 & 501 & 212.35 & 0.00\% & 175.3 \\ \hline
\end{tabulary}
\caption{Throughput and Latency of All test cases with 15min data while enabled \acrshort{k8s} Auto Scaling}
\label{tab:obs_all_auto_15_min_summary}
\end{table}
\ref{tab:obs_all_auto_15_min_summary} shows the response latency summary details and \acrshort{rps} as same as explained in \ref{subse:obs_test_plan_all_15min}.
During this test plan. the main focus on the auto scaling enabled microservice. As per the insert grid latency in the \ref{tab:obs_all_auto_15_min_summary}, the average insert latency is reduced from 91ms to 87ms. Also error percentage reduced from 1.42\% to 0.18\%. Standard deviation reduced from 19.58 to 14.07 which means the latency is much closer to the average latency. These improvements in insert Grid timeseries data seems to affect on out put of retrieve Grid timeseries data as well.

@@

\subsection{Query module load test}
\label{subse:obs_test_plan_query_15min}
This section \ref{subse:obs_test_plan_query_15min} discussed about the Query test plan performance. It performs multiple information retrieval queries such as query over locations, parameters and timeseries etc which are described over \ref{se:query}. It performed approximately 123k of sample requests.
Query test plan perform over 5 minutes of time period, and with a higher number of requests than other test plan with a peak of 600 hits per seconds.

\begin{table}[]
\begin{tabulary}{\linewidth}{|L|C|C|C|C|C|C|C|C|}
\hline
Label & Samples & Avg & Min & Max & 90\% Line & Std. Dev. & Error \% & RPS \\ \hline
* → Locations & 11462 & 992 & 5 & 17569 & 1740 & 704.67 & 0.00\% & 38.3 \\ \hline
Area → Locations & 11390 & 599 & 2 & 16755 & 1047 & 514.68 & 0.00\% & 38.1 \\ \hline
Location → Parameters & 11350 & 666 & 1 & 16821 & 1179 & 632.86 & 0.00\% & 38.0 \\ \hline
Locations → Parameters & 11305 & 659 & 1 & 17459 & 1149 & 678.55 & 0.00\% & 37.8 \\ \hline
Location → Timeseries & 11269 & 647 & 2 & 32693 & 1102 & 746.51 & 0.00\% & 37.7 \\ \hline
Locations → Timeseries & 11237 & 669 & 1 & 32651 & 1162 & 889.18 & 0.00\% & 37.6 \\ \hline
Locations, Parameter → Timeseries & 11192 & 662 & 2 & 32806 & 1152 & 789.49 & 0.00\% & 37.4 \\ \hline
Area → Timeseries & 11135 & 820 & 2 & 33235 & 1461 & 877.68 & 0.00\% & 37.3 \\ \hline
Area, Parameter → Timeseries & 11084 & 864 & 1 & 16699 & 1584 & 751.00 & 0.00\% & 37.1 \\ \hline
*, Parameter → Timeseries & 11011 & 696 & 2 & 16689 & 1216 & 693.33 & 0.00\% & 36.8 \\ \hline
* → Timeseries & 10968 & 1473 & 24 & 18283 & 2467 & 912.45 & 0.00\% & 36.7 \\ \hline
\textbf{TOTAL} & 123403 & 794 & 1 & 33235 & 1536 & 789.76 & 0.00\% & 412.6 \\ \hline
\end{tabulary}
\caption{Throughput and Latency of Query test cases with 15min data}
\label{tab:obs_query_15_min_summary}
\end{table}
\ref{tab:obs_query_15_min_summary} shows the response latency summary details. The average latency is much higher than the minimum value. Also it reported higher maximum values as well. Standard deviation showed as quiet higher value which means the response latency values are not closer to the average value. Noticeably, it does not reported any errors, which means all the requests successfully process.
The throughput for each test case is much higher and similar to all the requests. This is happening since all of these requests are handle via the adapter-query, it depends on the \acrshort{mongodb} database performance.

>>>>

\db{Sections \ref{subse:obs_test_plan_all_60min} to \ref{subse:obs_test_plan_all_auto_15min} discuss} the observations collected with performing the Load test plans over 60 minutes (24 data points), 30 minutes (48 data points) and 15 minutes (96 data points) by variate the request size. Then another performance test with enabling Auto Scaling as explained in \ref{subse:test_plan_metrics} for high resource utilized microservice.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Load Testing with hourly data (24 Request Size)}
\label{subse:obs_test_plan_all_60min}

@@

\begin{table}[ht]
\footnotesize
\begin{tabulary}{\linewidth}{|L|C|C|C|C|C|C|C|C|}
\hline
Label & \# Samples & Avg & Min & Max & 90\% Line & Std. Dev. & Error \% & RPS \\ \hline
Insert Timeseries & 71826 & 28 & 13 & 2773 & 31 & 58.74 & 0.00\% & 40.5 \\ \hline
Retrieve Timeseries & 71796 & 8 & 7 & 242 & 10 & 4.18 & 0.00\% & 40.7 \\ \hline
Insert Grid & 7982 & 23 & 21 & 126 & 26 & 4.23 & 0.06\% & 4.5 \\ \hline
Retrieve Grid & 7979 & 68 & 59 & 238 & 75 & 10.11 & 0.00\% & 4.5 \\ \hline
Query: Location & 71804 & 3 & 2 & 109 & 3 & 1.52 & 0.00\% & 40.5 \\ \hline
\textbf{TOTAL} & 311182 & 127 & 0 & 2773 & 503 & 207.80 & 0.00\% & 175.4 \\ \hline
\end{tabulary}
\caption{Throughput and Latency of All test cases with 60min data}
\label{tab:obs_all_60_min_summary}
\end{table}
Insert Timeseries performed over Scalar and Vector data types with each request send with 24 data points. On average it takes 28ms to insert data into the \acrshort{wdias}, and up to 90\% percentile inserted data within 31ms. Noticeably it has 0\% of errors which means that all the request are completed successfully. On average, \acrshort{wdias} handled 40.5 \acrshort{rps} with the given workload. The performance of the Retrieve of Scalar and Vector Timeseries are similar to insert timeseries due to it depends on it.
On the other hand, Insert Grid Timeseries data perform with 23ms with almost all the request perform within same amount of time, hence the standard deviation is smaller. Retrieve Grid Timeseries data perform the same but with bit higher value of latency of 68ms. Both of insert and retrieve grid timeseries data have 4.5 \acrshort{rps} since it only get 10\% of the number of request per given time via the test plan as explain in the data ration in \ref{se:test_plan}.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Load Testing with 30min data (48 Request Size)}
\label{subse:obs_test_plan_all_30min}
This section \ref{subse:obs_test_plan_all_30min} discussed about the All test plan performance with 30 minutes data which means 48 data points per each request in Scalar and Vector timeseries, and 48 ASCII Grid files per each insert request. It performed round up to 311k of sample requests which is almost similar to \ref{subse:obs_test_plan_all_60min} processed samples.
\begin{table}[ht]
\footnotesize
\begin{tabulary}{\linewidth}{|L|C|C|C|C|C|C|C|C|}
\hline
Label & \# Samples & Average & Min & Max & 90\% Line & Std. Dev. & Error \% & RPS \\ \hline
Insert Timeseries & 71759 & 29 & 14 & 1699 & 32 & 50.97 & 0.00\% & 40.5 \\ \hline
Retrieve Timeseries & 71730 & 9 & 7 & 1033 & 10 & 6.04 & 0.00\% & 40.6 \\ \hline
Insert Grid & 7972 & 44 & 40 & 162 & 49 & 8.17 & 0.08\% & 4.5 \\ \hline
Retrieve Grid & 7971 & 81 & 67 & 284 & 93 & 15.15 & 0.00\% & 4.5 \\ \hline
Query: Location & 71734 & 3 & 2 & 110 & 3 & 1.90 & 0.00\% & 40.5 \\ \hline
TOTAL & 310878 & 129 & 0 & 1699 & 503 & 207.10 & 0.00\% & 175.3 \\ \hline
\end{tabulary}
\caption{Throughput and Latency of All test cases with 30min data}
\label{tab:obs_all_30_min_summary}
\end{table}
\ref{tab:obs_all_30_min_summary} shows the response latency summary details and \acrshort{rps} as explained in \ref{subse:obs_test_plan_all_60min}. And the results are almost similar to the observations in \ref{tab:obs_all_60_min_summary}. This implies that, even the request size is increased, the \acrshort{wdias} can perform better same as the with smaller size of data.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Load Testing with 15min data (96 Request Size)}
\label{subse:obs_test_plan_all_15min}
This section \ref{subse:obs_test_plan_all_15min} discussed about the All test plan performance with 15 minutes data which means 96 data points per each request in Scalar and Vector timeseries, and 96 ASCII Grid files per each insert Grid timeseries request. These requests are four times larger than the \ref{subse:obs_test_plan_all_60min} request size. It performed approximately 311k of sample requests which is almost similar to \ref{subse:obs_test_plan_all_30min} processed samples.
\begin{table}[ht]
\footnotesize
\begin{tabulary}{\linewidth}{|L|C|C|C|C|C|C|C|C|}
\hline
Label & \# Samples & Average & Min & Max & 90\% Line & Std. Dev. & Error \% & RPS \\ \hline
Insert Timeseries & 71775 & 30 & 12 & 1719 & 41 & 51.71 & 0.00\% & 40.5 \\ \hline
Retrieve Timeseries & 71736 & 23 & 8 & 1623 & 32 & 50.18 & 0.00\% & 40.6 \\ \hline
Insert Grid & 7975 & 91 & 77 & 279 & 112 & 19.58 & 1.42\% & 4.5 \\ \hline
Retrieve Grid & 7972 & 118 & 80 & 876 & 165 & 56.15 & 0.00\% & 4.5 \\ \hline
Query: Location & 71749 & 3 & 2 & 130 & 4 & 2.32 & 0.00\% & 40.5 \\ \hline
\textbf{TOTAL} & 310934 & 134 & 0 & 1719 & 503 & 206.40 & 0.04\% & 175.4 \\ \hline
\end{tabulary}
\caption{Throughput and Latency of All test cases with 15min data}
\label{tab:obs_all_15_min_summary}
\end{table}
\ref{tab:obs_all_15_min_summary} shows the response latency summary details and \acrshort{rps} as same as explained in \ref{subse:obs_test_plan_all_30min}. And the latency observations are increased by some amount when compared to the observations in \ref{tab:obs_all_30_min_summary}. Noticeably retrieving latency of all type of data types increased by considerable amount. Same following the trend, standard deviation of retrieve timeseries data increased my considerable amount for all the types. We can assume that more writing to the databases affected on reads as well. Event the request data size increased by 4x time, the \acrshort{wdias} were able to handle them without any significant performance issues. And the system able to provide the same throughput as \ref{tab:obs_all_30_min_summary}.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Full Load test with \acrfull{k8s} auto pod scaling}
\label{subse:obs_test_plan_all_auto_15min}
This section \ref{subse:obs_test_plan_all_auto_15min} discussed about the All test plan performance with 15 minutes data which means 96 data points per each request in Scalar and Vector timeseries, and 96 ASCII Grid files per each insert Grid timeseries request. These requests are four times larger than the \ref{subse:obs_test_plan_all_60min} request size. It performed approximately 311k of sample requests which is almost similar to \ref{subse:obs_test_plan_all_15min} processed samples.
Other than that, this test plan runs with enabling \acrshort{k8s} Auto Scaling for the high resource utilized microservice as explained in the \ref{subse:test_plan_metrics}. With the test load used for the performance test, import-ascii-grid-upload microservice is using lots of CPU, and adapter-grid microservice is using lots of Memory. During this test plan, \acrshort{wdias} start with the auto scaling enabled for import-ascii-grid-upload microservice. Since adapter-grid is a consistence service for storing netCDF files, it is not possible to auto scale, since \acrshort{eks} does not support multiple read write support volumes \cite{LinuxFoundationPersistentKubernetes}.

\begin{table}[ht]
\footnotesize
\begin{tabulary}{\linewidth}{|L|C|C|C|C|C|C|C|C|}
\hline
Label & Samples & Avg & Min & Max & 90\% Line & Std. Dev. & Error \% & RPS \\ \hline
Insert Timeseries & 71727 & 34 & 13 & 1777 & 27 & 118.78 & 0.00\% & 40.5 \\ \hline
Retrieve Timeseries & 71693 & 7 & 5 & 1608 & 9 & 18.72 & 0.00\% & 40.5 \\ \hline
Insert Grid & 7968 & 87 & 77 & 233 & 98 & 14.07 & 0.18\% & 4.5 \\ \hline
Retrieve Grid & 7965 & 89 & 63 & 1694 & 110 & 37.79 & 0.00\% & 4.5 \\ \hline
Query: Location & 71704 & 1 & 0 & 203 & 2 & 2.05 & 0.00\% & 40.5 \\ \hline
\textbf{TOTAL} & 310734 & 130 & 0 & 1777 & 501 & 212.35 & 0.00\% & 175.3 \\ \hline
\end{tabulary}
\caption{Throughput and Latency of All test cases with 15min data while enabled \acrshort{k8s} Auto Scaling}
\label{tab:obs_all_auto_15_min_summary}
\end{table}
\ref{tab:obs_all_auto_15_min_summary} shows the response latency summary details and \acrshort{rps} as same as explained in \ref{subse:obs_test_plan_all_15min}.
During this test plan. the main focus on the auto scaling enabled microservice. As per the insert grid latency in the \ref{tab:obs_all_auto_15_min_summary}, the average insert latency is reduced from 91ms to 87ms. Also error percentage reduced from 1.42\% to 0.18\%. Standard deviation reduced from 19.58 to 14.07 which means the latency is much closer to the average latency. These improvements in insert Grid timeseries data seems to affect on out put of retrieve Grid timeseries data as well.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Query module load test}
\label{subse:obs_test_plan_query_15min}
This section \ref{subse:obs_test_plan_query_15min} discussed about the Query test plan performance. It performs multiple information retrieval queries such as query over locations, parameters and timeseries etc which are described over \ref{se:query}. It performed approximately 123k of sample requests.
Query test plan perform over 5 minutes of time period, and with a higher number of requests than other test plan with a peak of 600 hits per seconds.

\begin{table}[ht]
\footnotesize
\begin{tabulary}{\linewidth}{|L|C|C|C|C|C|C|C|C|}
\hline
Label & Samples & Avg & Min & Max & 90\% Line & Std. Dev. & Error \% & RPS \\ \hline
* → Locations & 11462 & 992 & 5 & 17569 & 1740 & 704.67 & 0.00\% & 38.3 \\ \hline
Area → Locations & 11390 & 599 & 2 & 16755 & 1047 & 514.68 & 0.00\% & 38.1 \\ \hline
Location → Parameters & 11350 & 666 & 1 & 16821 & 1179 & 632.86 & 0.00\% & 38.0 \\ \hline
Locations → Parameters & 11305 & 659 & 1 & 17459 & 1149 & 678.55 & 0.00\% & 37.8 \\ \hline
Location → Timeseries & 11269 & 647 & 2 & 32693 & 1102 & 746.51 & 0.00\% & 37.7 \\ \hline
Locations → Timeseries & 11237 & 669 & 1 & 32651 & 1162 & 889.18 & 0.00\% & 37.6 \\ \hline
Locations, Parameter → Timeseries & 11192 & 662 & 2 & 32806 & 1152 & 789.49 & 0.00\% & 37.4 \\ \hline
Area → Timeseries & 11135 & 820 & 2 & 33235 & 1461 & 877.68 & 0.00\% & 37.3 \\ \hline
Area, Parameter → Timeseries & 11084 & 864 & 1 & 16699 & 1584 & 751.00 & 0.00\% & 37.1 \\ \hline
*, Parameter → Timeseries & 11011 & 696 & 2 & 16689 & 1216 & 693.33 & 0.00\% & 36.8 \\ \hline
* → Timeseries & 10968 & 1473 & 24 & 18283 & 2467 & 912.45 & 0.00\% & 36.7 \\ \hline
\textbf{TOTAL} & 123403 & 794 & 1 & 33235 & 1536 & 789.76 & 0.00\% & 412.6 \\ \hline
\end{tabulary}
\caption{Throughput and Latency of Query test cases with 15min data}
\label{tab:obs_query_15_min_summary}
\end{table}
\ref{tab:obs_query_15_min_summary} shows the response latency summary details. The average latency is much higher than the minimum value. Also it reported higher maximum values as well. Standard deviation showed as quiet higher value which means the response latency values are not closer to the average value. Noticeably, it does not reported any errors, which means all the requests successfully process.
The throughput for each test case is much higher and similar to all the requests. This is happening since all of these requests are handle via the adapter-query, it depends on the \acrshort{mongodb} database performance.

### 2020-02-10 results/sec_4-discussion.tex
Change Full Test

\section{Discussion}

\dbc{It's odd to add a conclusion only for this chapter. If this is more of a discussion, name it as Discussion.}

@@

\paragraph{Latency}
The latency for each operation type kept constant over the whole test plan run time without any significant change. When the request size increased from 24 data points to 96 data points, the latency increase throw out the whole test plan with a smaller number. But for each test run the latency kept constant over the time.
During the \ref{subse:obs_test_plan_all_auto_15min} test run, the performance of the Grid data got better when compared to the \ref{subse:obs_test_plan_all_15min}. Which means by adding more resources to the \acrshort{wdias}, it can handle more workload on the system.

\paragraph{Throughput}
While keeping the latency constant without significant change, the throughput of the \acrshort{wdias} kept constant while increasing the request size from 60min data (24 data points) to 15min data (96 data points) for all the data types such as Scalar, Vector and Grid.
When number of active threads increased, the \acrshort{wdias} able to provide the same throughput with maintaining the latency stable.

@@

\paragraph{Resource Utilization}
Since \acrshort{wdias} using the \acrshort{k8s} as the container orchestration system, it allows to scale up and cool down the system as required based on the workload. This demonstrate on the test plan of \ref{subse:obs_test_plan_all_auto_15min}, and the system get scale up to the maximum at the peak time. Then cool down to single pod after finishing the test cases.
Given above \acrshort{wdias} can run from 1 CPU node to nodes with 100 CPUs. As described in the \ref{se:microservice}, it uses the many of the concept of modern microservice architecture to create stateless, failover, redundant microservice to achieve such capabilities.

\paragraph{Auto Scaling}
The \acrshort{wdias} supports auto scaling by out of the box with \acrshort{k8s}. Services can configure with maximum number of pods in order to avoid over resource usage. When there is not much workload on the system, system cool down to less pods in order to save more resources. When there is any issue with a pod, \acrshort{k8s} auto schedule another pod and remove the unhealthy pod. Also it allows to update the system without any down time with rollback updates.

\paragraph{Risk of Unable to Process Data}
During the test performance, the \acrshort{wdias} processed many requests with higher request size than the normal usage with lower rate of failures to process the requests, mainly with insert Grid data. If the usage of \acrshort{wdias} want to reduce the risk of unable to process data, then system can configure to run with redundant pods in order to handle spike of workloads. Also while configure for the auto scaling, the \acrshort{k8s} can configure to maintain lower amount of CPU usage such as 50\% to 60\% rather 80\%. Such configuration with always spawn new pods to handle double of current peak load.

>>>>

\section{Performance Metrics Analysis}

@@

The \emph{Latency} for each operation type kept constant over the whole test plan run time without any significant change. When the request size increased from 24 data points to 96 data points, the latency increase throw out the whole test plan with a smaller number. But for each test run the latency kept constant over the time.
During the \ref{subse:obs_test_plan_all_auto_15min} test run, the performance of the Grid data got better when compared to the \ref{subse:obs_test_plan_all_15min}. Which means by adding more resources to the \acrshort{wdias}, it can handle more workload on the system.

While keeping the latency constant without significant change, the \emph{throughput} of the \acrshort{wdias} kept constant while increasing the request size from 60min data (24 data points) to 15min data (96 data points) for all the data types such as Scalar, Vector and Grid.
When number of active threads increased, the \acrshort{wdias} able to provide the same throughput with maintaining the latency stable.

@@

When look into the \emph{resource utilization} of \acrshort{wdias}; since it is using the \acrshort{k8s} as the container orchestration system, it allows to scale up and cool down the system as required based on the workload. This demonstrate on the test plan of \ref{subse:obs_test_plan_all_auto_15min}, and the system get scale up to the maximum at the peak time. Then cool down to single pod after finishing the test cases.
Given above \acrshort{wdias} can run from 1 CPU node to nodes with 100 CPUs. As described in the \ref{se:microservice}, it uses the many of the concept of modern microservice architecture to create stateless, failover, redundant microservice to achieve such capabilities.

The \acrshort{wdias} supports \emph{auto scaling} by out of the box with \acrshort{k8s}. Services can configure with maximum number of pods in order to avoid over resource usage. When there is not much workload on the system, system cool down to less pods in order to save more resources. When there is any issue with a pod, \acrshort{k8s} auto schedule another pod and remove the unhealthy pod. Also it allows to update the system without any down time with rollback updates.

\emph{Risk of unable to process data} during the test performance, the \acrshort{wdias} processed many requests with higher request size than the normal usage with lower rate of failures to process the requests, mainly with insert Grid data. If the usage of \acrshort{wdias} want to reduce the risk of unable to process data, then system can configure to run with redundant pods in order to handle spike of workloads. Also while configure for the auto scaling, the \acrshort{k8s} can configure to maintain lower amount of CPU usage such as 50\% to 60\% rather 80\%. Such configuration with always spawn new pods to handle double of current peak load.
